Project Setup

### 2025-01-27 setup.qmd
Clarify usage of renv
Fix citations
Somehow the order of citations changes, thus
moving the "e.g." around. Now we cite them
directly in the order they appear later on.

Also, we will utilize the package [`renv`](https://rstudio.github.io/renv/) to track the R packages our project depends on. Using it makes it easier for others to view and obtain them at a later point in time. Therefore make sure that the box _Use renv with this project_ is checked. Again, if this is the first time you are hearing about `renv`, have a look at the tutorial "[Introduction to {renv}](https://lmu-osc.github.io/introduction-to-renv/)".

@@

Throughout this tutorial, you will need to run both R code and system commands (primarily `git` and `quarto`). Within RStudio, R code can be run by going to the tab _Console_, while system commands are executed in the tab _Terminal_. We also indicate where to run your code directly above each code snippet.

@@

Luckily, there are already numerous proposals for how to organize one's project files, both general [e.g., @Wilson2017; @TIER4] as well as specific to a particular programming language [e.g., @Marwick2018; @Vuorre2021; @ArayaSalas2024] or journal [@Vilhuber2021]. We recommend you to follow the standards of your field.

>>>>

Also, we will utilize the package [`renv`](https://rstudio.github.io/renv/) to track the R packages our project depends on. Using it makes it easier for others to view and obtain them at the exact same version at a later point in time. Therefore make sure that the box _Use renv with this project_ is checked. Again, if this is the first time you are hearing about `renv`, have a look at the tutorial "[Introduction to {renv}](https://lmu-osc.github.io/introduction-to-renv/)".

@@

Throughout this tutorial, you will need to run both R code and system commands (primarily `git` and `quarto`). Within RStudio, R code can be run by going to the tab _Console_, while system commands are executed in the tab _Terminal_. We also indicate where to run your code directly above each code snippet. If no indication is given, the code is only for demonstration purposes and does not need to be run.

@@

Luckily, there are already numerous proposals for how to organize one's project files, both general [e.g., @TIER4; @Wilson2017] as well as specific to a particular programming language [e.g., @ArayaSalas2024; @Marwick2018; @Vuorre2021] or journal [@Vilhuber2021]. We recommend you to follow the standards of your field.
